Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-18 paper.qmd
some changes made after last commit

      color = "black") 

@@

```{r}
#| label: fig-hex-param
#| fig-cap: "The components of the hexagon grid illustrating notation."
#| out-height: 30%
#| fig-width: 2.5
#| fig-height: 3.3
#| fig-pos: H

>>>>

  coord_equal()

@@

```{r}
#| label: fig-hex-param
#| fig-cap: "The components of the hexagon grid illustrating notation."
#| out-height: 30%
#| fig-pos: H
